clusters

### 2015-07-17 cluster.rmd
knn start

# library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
# library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')

# library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
library('FNN')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')

# library('RcmdrPlugin.BCA')
# library(devtools)
# library('ggbiplot')
# library('fpc')
# library('vegan')
# library('knitr')
# library('ggplot2')
# library("plyr")
# library("dplyr")
# library('magrittr')
# library('reshape2')
# library("rpart")
# library('car')
# library('e1071')
# library('corrgram')
# library('party')
# library('dendextend')
# library('FNN')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
# all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

Retrieve nearest neighbour

```{r knn, echo=FALSE}
